---
title: "orbweaver"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(orbweaver)
```

orbweaver helps you to build, manipulate and analyze directed and acyclic 
graphs in R.

### Build

* `graph_builder()` initiates the process of building a graph.
* `add_edge()` adds a directed edge between two nodes.
* `add_path()` adds a path to the graph.
* `build_directed()` finalizes the graph as a directed graph.

```{r}
graph <- graph_builder() |>
  add_edge(from = "a", to = "b") |>
  add_edge(from = "a", to = "c") |>
  add_edge(from = "b", to = "d") |>
  add_edge(from = "c", to = "d") |>
  add_path(path = c("a", "b", "d")) |>
  build_directed()
graph
```

* `populate_edges()` populates edges of a graph from a data frame.
* `build_acyclic()` finalizes the graph as an acyclic graph.

```{r}
edges <- data.frame(
  parent = c("a", "a", "b", "c"),
  child = c("b", "c", "d", "d")
)

acyclic_graph <- graph_builder() |>
  populate_edges(edges_df = edges, parent_col = parent, child_col = child) |>
  build_acyclic()
acyclic_graph
```

### i/o

* `graph_to_bin()` writes a graph to a file or memory.
* `graph_from_bin()` reads a graph from a file or memory.

```{r}
file <- tempfile()
graph_to_bin(graph, path = file)
graph_from_bin(path = file, type = "directed")

bin <- graph_to_bin(graph)
graph_from_bin(bin = bin, type = "directed")
```

### Explore

* `has_children()` checks whether a node has children.

```{r}
has_children(graph, nodes = "a")
has_children(graph, nodes = "d")
```

* `has_parents()` checks whether a node has parents.

```{r}
has_parents(graph, nodes = "a")
has_parents(graph, nodes = "d")
```

* `subset()` subsets a graph to include only specific nodes.

```{r}
subset(graph, nodes = c("a", "b", "d"))
```

* `length()` returns the number of nodes in a graph.

```{r}
length(graph)
```

* `nodes()` returns all nodes in a graph.

```{r}
nodes(graph)
```

* `children()` returns the children of a specific node in a graph.

```{r}
children(graph, node = "a")
```

* `parents()` returns the parents of a specific node in a graph.

```{r}
parents(graph, node = "d")
```

### Analyze

* `find_path()` finds a path between two nodes.

```{r}
find_path(graph, from = "a", to = "d")
```

* `find_all_paths()` finds all paths between two nodes.

```{r}
find_all_paths(graph, from = "a", to = "d")
```

* `find_path_one_to_many()` finds a valid path from one node to multiple 
destinations in a directed graph.

```{r}
find_path_one_to_many(acyclic_graph, from = "a", to = edges$child)
```

* `get_all_leaves()` returns all leaf nodes in a graph.

```{r}
get_all_leaves(graph)
```

* `get_all_roots()` returns all root nodes in a graph.

```{r}
get_all_roots(graph)
```

* `get_leaves_under()` returns all leaf nodes under a specific node in a graph.

```{r}
get_leaves_under(graph, node = "a")
```

* `get_roots_over()` returns all root nodes over a specific node in a graph.

```{r}
get_roots_over(graph, node = "d")
```

* `least_common_parents()` returns the least common parents of a set of nodes in
a graph.

```{r}
least_common_parents(graph, selected = c("d", "c"))
```
